\textit{F1000Research} A studyforrest extension, an annotations of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-05 paper/main.tex
move column "description" to the left in all tableles

\begin{table*}[t]
\caption{Simple part of speech tagging (POS). All 15 categories sorted alpapetically. Descriptions were taken from spaCy.explain(). Non-speech vocalizations (NONSPEECH) were manually added.}
\label{tab:example}
\begin{tabular}{lllllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
\midrule
ADJ & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV & \aPosAdjV & \aPosAdjVI & \aPosAdjVII & \aPosAdjVIII & \aPosAdj \tabularnewline
ADP & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII & \aPosAdp\tabularnewline
ADV & \aPosAdvAll & \aPosAdvI & \aPosAdvII & \aPosAdvIII & \aPosAdvIV & \aPosAdvV & \aPosAdvVI & \aPosAdvVII & \aPosAdvVIII & \aPosAdv\tabularnewline
AUX & \aPosAuxAll & \aPosAuxI & \aPosAuxII & \aPosAuxIII & \aPosAuxIV & \aPosAuxV & \aPosAuxVI & \aPosAuxVII & \aPosAuxVIII & \aPosAux\tabularnewline
CONJ & \aPosConjAll & \aPosConjI & \aPosConjII & \aPosConjIII & \aPosConjIV & \aPosConjV & \aPosConjVI & \aPosConjVII & \aPosConjVIII & \aPosConj \tabularnewline
DET & \aPosDetAll & \aPosDetI & \aPosDetII & \aPosDetIII & \aPosDetIV & \aPosDetV & \aPosDetVI & \aPosDetVII & \aPosDetVIII & \aPosDet\tabularnewline
NONSPEECH  & \aPosNonspeechAll & \aPosNonspeechI & \aPosNonspeechII & \aPosNonspeechIII & \aPosNonspeechIV & \aPosNonspeechV & \aPosNonspeechVI & \aPosNonspeechVII & \aPosNonspeechVIII & non-speech vocalization \tabularnewline
NOUN & \aPosNounAll & \aPosNounI & \aPosNounII & \aPosNounIII & \aPosNounIV & \aPosNounV & \aPosNounVI & \aPosNounVII & \aPosNounVIII & \aPosNoun \tabularnewline
NUM & \aPosNumAll & \aPosNumI & \aPosNumII & \aPosNumIII & \aPosNumIV & \aPosNumV & \aPosNumVI & \aPosNumVII & \aPosNumVIII & \aPosNum\tabularnewline
PART & \aPosPartAll & \aPosPartI & \aPosPartII & \aPosPartIII & \aPosPartIV & \aPosPartV & \aPosPartVI & \aPosPartVII & \aPosPartVIII & \aPosPart \tabularnewline
PRON & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII & \aPosPron \tabularnewline
PRON  & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII & \aPosPropn \tabularnewline
SCONJ & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII & \aPosSconj \tabularnewline
VERB & \aPosVerbAll & \aPosVerbI & \aPosVerbII & \aPosVerbIII & \aPosVerbIV & \aPosVerbV & \aPosVerbVI & \aPosVerbVII & \aPosVerbVIII & \aPosVerb\tabularnewline
X & \aPosXAll & \aPosXI & \aPosXII & \aPosXIII & \aPosXIV & \aPosXV & \aPosXVI & \aPosXVII & \aPosXVIII & \aPosX \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Detailed part of speech tagging (TAG). The top 15 of 43 categories sorted alphabetically. Descriptions were taken from spaCy.explain().}
\label{tab:example}
\begin{tabular}{lllllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
\midrule
ADJA  & \aTagAdjaAll & \aTagAdjaI & \aTagAdjaII & \aTagAdjaIII & \aTagAdjaIV & \aTagAdjaV & \aTagAdjaVI & \aTagAdjaVII & \aTagAdjaVIII & \aTagAdja \tabularnewline
ADJD  & \aTagAdjdAll & \aTagAdjdI & \aTagAdjdII & \aTagAdjdIII & \aTagAdjdIV & \aTagAdjdV & \aTagAdjdVI & \aTagAdjdVII & \aTagAdjdVIII & \aTagAdjd \tabularnewline
ADV  & \aTagAdvAll & \aTagAdvI & \aTagAdvII & \aTagAdvIII & \aTagAdvIV & \aTagAdvV & \aTagAdvVI & \aTagAdvVII & \aTagAdvVIII & \aTagAdv \tabularnewline
APPR  & \aTagApprAll & \aTagApprI & \aTagApprII & \aTagApprIII & \aTagApprIV & \aTagApprV & \aTagApprVI & \aTagApprVII & \aTagApprVIII & \aTagAppr \tabularnewline
ART  & \aTagArtAll & \aTagArtI & \aTagArtII & \aTagArtIII & \aTagArtIV & \aTagArtV & \aTagArtVI & \aTagArtVII & \aTagArtVIII & \aTagArt \tabularnewline
KON  & \aTagKonAll & \aTagKonI & \aTagKonII & \aTagKonIII & \aTagKonIV & \aTagKonV & \aTagKonVI & \aTagKonVII & \aTagKonVIII & \aTagKon \tabularnewline
NE  & \aTagNeAll & \aTagNeI & \aTagNeII & \aTagNeIII & \aTagNeIV & \aTagNeV & \aTagNeVI & \aTagNeVII & \aTagNeVIII & \aTagNe \tabularnewline
NN  & \aTagNnAll & \aTagNnI & \aTagNnII & \aTagNnIII & \aTagNnIV & \aTagNnV & \aTagNnVI & \aTagNnVII & \aTagNnVIII & \aTagNn \tabularnewline
PPER  & \aTagPperAll & \aTagPperI & \aTagPperII & \aTagPperIII & \aTagPperIV & \aTagPperV & \aTagPperVI & \aTagPperVII & \aTagPperVIII & \aTagPper \tabularnewline
PPOSAT  & \aTagPposatAll & \aTagPposatI & \aTagPposatII & \aTagPposatIII & \aTagPposatIV & \aTagPposatV & \aTagPposatVI & \aTagPposatVII & \aTagPposatVIII & \aTagPposat \tabularnewline
PTKVZ  & \aTagPtkvzAll & \aTagPtkvzI & \aTagPtkvzII & \aTagPtkvzIII & \aTagPtkvzIV & \aTagPtkvzV & \aTagPtkvzVI & \aTagPtkvzVII & \aTagPtkvzVIII & \aTagPtkvz \tabularnewline
VAFIN  & \aTagVafinAll & \aTagVafinI & \aTagVafinII & \aTagVafinIII & \aTagVafinIV & \aTagVafinV & \aTagVafinVI & \aTagVafinVII & \aTagVafinVIII & \aTagVafin \tabularnewline
VVFIN  & \aTagVvfinAll & \aTagVvfinI & \aTagVvfinII & \aTagVvfinIII & \aTagVvfinIV & \aTagVvfinV & \aTagVvfinVI & \aTagVvfinVII & \aTagVvfinVIII & \aTagVvfin \tabularnewline
VVINF  & \aTagVvinfAll & \aTagVvinfI & \aTagVvinfII & \aTagVvinfIII & \aTagVvinfIV & \aTagVvinfV & \aTagVvinfVI & \aTagVvinfVII & \aTagVvinfVIII & \aTagVvinf \tabularnewline
VVPP  & \aTagVvppAll & \aTagVvppI & \aTagVvppII & \aTagVvppIII & \aTagVvppIV & \aTagVvppV & \aTagVvppVI & \aTagVvppVII & \aTagVvppVIII & \aTagVvpp \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Syntactic dependencies (DEP). The top 15 of 37 categories sorted alphabetically. Descriptions were taken from spaCy.explain().}
\label{tab:example}
\begin{tabular}{lllllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
\midrule
cd  & \aDepCdAll & \aDepCdI & \aDepCdII & \aDepCdIII & \aDepCdIV & \aDepCdV & \aDepCdVI & \aDepCdVII & \aDepCdVIII & \aDepCd \tabularnewline
cj  & \aDepCjAll & \aDepCjI & \aDepCjII & \aDepCjIII & \aDepCjIV & \aDepCjV & \aDepCjVI & \aDepCjVII & \aDepCjVIII & \aDepCj \tabularnewline
cp  & \aDepCpAll & \aDepCpI & \aDepCpII & \aDepCpIII & \aDepCpIV & \aDepCpV & \aDepCpVI & \aDepCpVII & \aDepCpVIII & \aDepCp \tabularnewline
da  & \aDepDaAll & \aDepDaI & \aDepDaII & \aDepDaIII & \aDepDaIV & \aDepDaV & \aDepDaVI & \aDepDaVII & \aDepDaVIII & \aDepDa \tabularnewline
ju  & \aDepJuAll & \aDepJuI & \aDepJuII & \aDepJuIII & \aDepJuIV & \aDepJuV & \aDepJuVI & \aDepJuVII & \aDepJuVIII & \aDepJu \tabularnewline
mnr  & \aDepMnrAll & \aDepMnrI & \aDepMnrII & \aDepMnrIII & \aDepMnrIV & \aDepMnrV & \aDepMnrVI & \aDepMnrVII & \aDepMnrVIII & \aDepMnr \tabularnewline
Mmo  & \aDepMoAll & \aDepMoI & \aDepMoII & \aDepMoIII & \aDepMoIV & \aDepMoV & \aDepMoVI & \aDepMoVII & \aDepMoVIII & \aDepMo \tabularnewline
nk  & \aDepNkAll & \aDepNkI & \aDepNkII & \aDepNkIII & \aDepNkIV & \aDepNkV & \aDepNkVI & \aDepNkVII & \aDepNkVIII & \aDepNk \tabularnewline
oa  & \aDepOaAll & \aDepOaI & \aDepOaII & \aDepOaIII & \aDepOaIV & \aDepOaV & \aDepOaVI & \aDepOaVII & \aDepOaVIII & \aDepOa \tabularnewline
oc  & \aDepOcAll & \aDepOcI & \aDepOcII & \aDepOcIII & \aDepOcIV & \aDepOcV & \aDepOcVI & \aDepOcVII & \aDepOcVIII & \aDepOc \tabularnewline
pd  & \aDepPdAll & \aDepPdI & \aDepPdII & \aDepPdIII & \aDepPdIV & \aDepPdV & \aDepPdVI & \aDepPdVII & \aDepPdVIII & \aDepPd \tabularnewline
pnc  & \aDepPncAll & \aDepPncI & \aDepPncII & \aDepPncIII & \aDepPncIV & \aDepPncV & \aDepPncVI & \aDepPncVII & \aDepPncVIII & \aDepPnc \tabularnewline
ROOT  & \aDepRootAll & \aDepRootI & \aDepRootII & \aDepRootIII & \aDepRootIV & \aDepRootV & \aDepRootVI & \aDepRootVII & \aDepRootVIII & root \tabularnewline
sb  & \aDepSbAll & \aDepSbI & \aDepSbII & \aDepSbIII & \aDepSbIV & \aDepSbV & \aDepSbVI & \aDepSbVII & \aDepSbVIII & \aDepSb \tabularnewline
svp  & \aDepSvpAll & \aDepSvpI & \aDepSvpII & \aDepSvpIII & \aDepSvpIV & \aDepSvpV & \aDepSvpVI & \aDepSvpVII & \aDepSvpVIII & separable verb prefix \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} &     \textbf{examples}\\

@@

body & \aDescrBodyAll & \aDescrBodyI & \aDescrBodyII & \aDescrBodyIII & \aDescrBodyIV & \aDescrBodyV & \aDescrBodyVI & \aDescrBodyVII & \aDescrBodyVIII & back, hip, shoulder; jacket, dress, shirt \tabularnewline
bodypart & \aDescrBodypartAll & \aDescrBodypartI & \aDescrBodypartII & \aDescrBodypartIII & \aDescrBodypartIV & \aDescrBodypartV & \aDescrBodypartVI & \aDescrBodypartVII & \aDescrBodypartVIII & arm, finger, leg, toe \tabularnewline
face  & \aDescrFaceAll & \aDescrFaceI & \aDescrFaceII & \aDescrFaceIII & \aDescrFaceIV & \aDescrFaceV & \aDescrFaceVI & \aDescrFaceVII & \aDescrFaceVIII & face, ear, nose, mouth \tabularnewline
female  & \aDescrFemaleAll & \aDescrFemaleI & \aDescrFemaleII & \aDescrFemaleIII & \aDescrFemaleIV & \aDescrFemaleV & \aDescrFemaleVI & \aDescrFemaleVII & \aDescrFemaleVIII & nurse, mother, woman \tabularnewline
females  & \aDescrFemalesAll & \aDescrFemalesI & \aDescrFemalesII & \aDescrFemalesIII & \aDescrFemalesIV & \aDescrFemalesV & \aDescrFemalesVI & \aDescrFemalesVII & \aDescrFemalesVIII & women \tabularnewline
fname  & \aDescrFnameAll & \aDescrFnameI & \aDescrFnameII & \aDescrFnameIII & \aDescrFnameIV & \aDescrFnameV & \aDescrFnameVI & \aDescrFnameVII & \aDescrFnameVIII & Jenny \tabularnewline
furniture  & \aDescrFurnitureAll & \aDescrFurnitureI & \aDescrFurnitureII & \aDescrFurnitureIII & \aDescrFurnitureIV & \aDescrFurnitureV & \aDescrFurnitureVI & \aDescrFurnitureVII & \aDescrFurnitureVIII & bench, bed, table, chair \tabularnewline
geo  & \aDescrGeoAll & \aDescrGeoI & \aDescrGeoII & \aDescrGeoIII & \aDescrGeoIV & \aDescrGeoV & \aDescrGeoVI & \aDescrGeoVII & \aDescrGeoVIII & building, tree, street, alley, meadow, cornfield, river \tabularnewline
geo-room  & \aDescrGeoroomAll & \aDescrGeoroomI & \aDescrGeoroomII & \aDescrGeoroomIII & \aDescrGeoroomIV & \aDescrGeoroomV & \aDescrGeoroomVI & \aDescrGeoroomVII & \aDescrGeoroomVIII & living room; wall, door, window, floor, turf \tabularnewline
head  & \aDescrHeadAll & \aDescrHeadI & \aDescrHeadII & \aDescrHeadIII & \aDescrHeadIV & \aDescrHeadV & \aDescrHeadVI & \aDescrHeadVII & \aDescrHeadVIII & head, hair, ear, neck, helmet \tabularnewline
male  & \aDescrMaleAll & \aDescrMaleI & \aDescrMaleII & \aDescrMaleIII & \aDescrMaleIV & \aDescrMaleV & \aDescrMaleVI & \aDescrMaleVII & \aDescrMaleVIII & man, father, soldier \tabularnewline
males  & \aDescrMalesAll & \aDescrMalesI & \aDescrMalesII & \aDescrMalesIII & \aDescrMalesIV & \aDescrMalesV & \aDescrMalesVI & \aDescrMalesVII & \aDescrMalesVIII & boys, opponents \tabularnewline
mname  & \aDescrMnameAll & \aDescrMnameI & \aDescrMnameII & \aDescrMnameIII & \aDescrMnameIV & \aDescrMnameV & \aDescrMnameVI & \aDescrMnameVII & \aDescrMnameVIII & Bubba, Kennedy \tabularnewline
object  & \aDescrObjectAll & \aDescrObjectI & \aDescrObjectII & \aDescrObjectIII & \aDescrObjectIV & \aDescrObjectV & \aDescrObjectVI & \aDescrObjectVII & \aDescrObjectVIII & telephone, car \tabularnewline
objects  & \aDescrObjectsAll & \aDescrObjectsI & \aDescrObjectsII & \aDescrObjectsIII & \aDescrObjectsIV & \aDescrObjectsV & \aDescrObjectsVI & \aDescrObjectsVII & \aDescrObjectsVIII & wheels, photos \tabularnewline
persons  & \aDescrPersonsAll & \aDescrPersonsI & \aDescrPersonsII & \aDescrPersonsIII & \aDescrPersonsIV & \aDescrPersonsV & \aDescrPersonsVI & \aDescrPersonsVII & \aDescrPersonsVIII & hippies, patients \tabularnewline

>>>>

\begin{table*}[t]
\caption{Simple part of speech tagging (POS). All 15 categories sorted alpapetically. Descriptions were taken from spaCy.explain(). Non-speech vocalizations (NONSPEECH) were manually added.}
\label{tab:example}
\begin{tabular}{lllllllllll}
\toprule
\textbf{category} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
ADJ & \aPosAdj & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV & \aPosAdjV & \aPosAdjVI & \aPosAdjVII \tabularnewline
ADP & \aPosAdp & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII \tabularnewline
ADV & \aPosAdv & \aPosAdvAll & \aPosAdvI & \aPosAdvII & \aPosAdvIII & \aPosAdvIV & \aPosAdvV & \aPosAdvVI & \aPosAdvVII & \aPosAdvVIII \tabularnewline
AUX & \aPosAux & \aPosAuxAll & \aPosAuxI & \aPosAuxII & \aPosAuxIII & \aPosAuxIV & \aPosAuxV & \aPosAuxVI & \aPosAuxVII & \aPosAuxVIII \tabularnewline
CONJ & \aPosConj & \aPosConjAll & \aPosConjI & \aPosConjII & \aPosConjIII & \aPosConjIV & \aPosConjV & \aPosConjVI & \aPosConjVII & \aPosConjVIII \tabularnewline
DET & \aPosDet & \aPosDetAll & \aPosDetI & \aPosDetII & \aPosDetIII & \aPosDetIV & \aPosDetV & \aPosDetVI & \aPosDetVII & \aPosDetVIII \tabularnewline
NONSPEECH & non-speech vocalization & \aPosNonspeechAll & \aPosNonspeechI & \aPosNonspeechII & \aPosNonspeechIII & \aPosNonspeechIV & \aPosNonspeechV & \aPosNonspeechVI & \aPosNonspeechVII & \aPosNonspeechVIII \tabularnewline
NOUN & \aPosNoun & \aPosNounAll & \aPosNounI & \aPosNounII & \aPosNounIII & \aPosNounIV & \aPosNounV & \aPosNounVI & \aPosNounVII & \aPosNounVIII \tabularnewline
NUM & \aPosNum & \aPosNumAll & \aPosNumI & \aPosNumII & \aPosNumIII & \aPosNumIV & \aPosNumV & \aPosNumVI & \aPosNumVII & \aPosNumVIII \tabularnewline
PART & \aPosPart & \aPosPartAll & \aPosPartI & \aPosPartII & \aPosPartIII & \aPosPartIV & \aPosPartV & \aPosPartVI & \aPosPartVII & \aPosPartVIII \tabularnewline
PRON & \aPosPron & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII \tabularnewline
PRON & \aPosPropn & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII \tabularnewline
SCONJ & \aPosSconj & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII \tabularnewline
VERB & \aPosVerb & \aPosVerbAll & \aPosVerbI & \aPosVerbII & \aPosVerbIII & \aPosVerbIV & \aPosVerbV & \aPosVerbVI & \aPosVerbVII & \aPosVerbVIII \tabularnewline
X & \aPosX & \aPosXAll & \aPosXI & \aPosXII & \aPosXIII & \aPosXIV & \aPosXV & \aPosXVI & \aPosXVII & \aPosXVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Detailed part of speech tagging (TAG). The top 15 of 43 categories sorted alphabetically. Descriptions were taken from spaCy.explain().}
\label{tab:example}
\begin{tabular}{lllllllllll}
\toprule
\textbf{category} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
ADJA & \aTagAdja & \aTagAdjaAll & \aTagAdjaI & \aTagAdjaII & \aTagAdjaIII & \aTagAdjaIV & \aTagAdjaV & \aTagAdjaVI & \aTagAdjaVII & \aTagAdjaVIII \tabularnewline
ADJD & \aTagAdjd & \aTagAdjdAll & \aTagAdjdI & \aTagAdjdII & \aTagAdjdIII & \aTagAdjdIV & \aTagAdjdV & \aTagAdjdVI & \aTagAdjdVII & \aTagAdjdVIII \tabularnewline
ADV & \aTagAdv & \aTagAdvAll & \aTagAdvI & \aTagAdvII & \aTagAdvIII & \aTagAdvIV & \aTagAdvV & \aTagAdvVI & \aTagAdvVII & \aTagAdvVIII \tabularnewline
APPR & \aTagAppr & \aTagApprAll & \aTagApprI & \aTagApprII & \aTagApprIII & \aTagApprIV & \aTagApprV & \aTagApprVI & \aTagApprVII & \aTagApprVIII \tabularnewline
ART & \aTagArt & \aTagArtAll & \aTagArtI & \aTagArtII & \aTagArtIII & \aTagArtIV & \aTagArtV & \aTagArtVI & \aTagArtVII & \aTagArtVIII \tabularnewline
KON & \aTagKon & \aTagKonAll & \aTagKonI & \aTagKonII & \aTagKonIII & \aTagKonIV & \aTagKonV & \aTagKonVI & \aTagKonVII & \aTagKonVIII \tabularnewline
NE & \aTagNe & \aTagNeAll & \aTagNeI & \aTagNeII & \aTagNeIII & \aTagNeIV & \aTagNeV & \aTagNeVI & \aTagNeVII & \aTagNeVIII \tabularnewline
NN & \aTagNn & \aTagNnAll & \aTagNnI & \aTagNnII & \aTagNnIII & \aTagNnIV & \aTagNnV & \aTagNnVI & \aTagNnVII & \aTagNnVIII \tabularnewline
PPER & \aTagPper & \aTagPperAll & \aTagPperI & \aTagPperII & \aTagPperIII & \aTagPperIV & \aTagPperV & \aTagPperVI & \aTagPperVII & \aTagPperVIII \tabularnewline
PPOSAT & \aTagPposat & \aTagPposatAll & \aTagPposatI & \aTagPposatII & \aTagPposatIII & \aTagPposatIV & \aTagPposatV & \aTagPposatVI & \aTagPposatVII & \aTagPposatVIII \tabularnewline
PTKVZ & \aTagPtkvz & \aTagPtkvzAll & \aTagPtkvzI & \aTagPtkvzII & \aTagPtkvzIII & \aTagPtkvzIV & \aTagPtkvzV & \aTagPtkvzVI & \aTagPtkvzVII & \aTagPtkvzVIII \tabularnewline
VAFIN & \aTagVafin & \aTagVafinAll & \aTagVafinI & \aTagVafinII & \aTagVafinIII & \aTagVafinIV & \aTagVafinV & \aTagVafinVI & \aTagVafinVII & \aTagVafinVIII \tabularnewline
VVFIN & \aTagVvfin & \aTagVvfinAll & \aTagVvfinI & \aTagVvfinII & \aTagVvfinIII & \aTagVvfinIV & \aTagVvfinV & \aTagVvfinVI & \aTagVvfinVII & \aTagVvfinVIII \tabularnewline
VVINF & \aTagVvinf & \aTagVvinfAll & \aTagVvinfI & \aTagVvinfII & \aTagVvinfIII & \aTagVvinfIV & \aTagVvinfV & \aTagVvinfVI & \aTagVvinfVII & \aTagVvinfVIII \tabularnewline
VVPP & \aTagVvpp & \aTagVvppAll & \aTagVvppI & \aTagVvppII & \aTagVvppIII & \aTagVvppIV & \aTagVvppV & \aTagVvppVI & \aTagVvppVII & \aTagVvppVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\caption{Syntactic dependencies (DEP). The top 15 of 37 categories sorted alphabetically. Descriptions were taken from spaCy.explain().}
\label{tab:example}
\begin{tabular}{lllllllllll}
\toprule
\textbf{category} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
cd & \aDepCd & \aDepCdAll & \aDepCdI & \aDepCdII & \aDepCdIII & \aDepCdIV & \aDepCdV & \aDepCdVI & \aDepCdVII & \aDepCdVIII \tabularnewline
cj & \aDepCj & \aDepCjAll & \aDepCjI & \aDepCjII & \aDepCjIII & \aDepCjIV & \aDepCjV & \aDepCjVI & \aDepCjVII & \aDepCjVIII \tabularnewline
cp & \aDepCp & \aDepCpAll & \aDepCpI & \aDepCpII & \aDepCpIII & \aDepCpIV & \aDepCpV & \aDepCpVI & \aDepCpVII & \aDepCpVIII \tabularnewline
da & \aDepDa & \aDepDaAll & \aDepDaI & \aDepDaII & \aDepDaIII & \aDepDaIV & \aDepDaV & \aDepDaVI & \aDepDaVII & \aDepDaVIII \tabularnewline
ju & \aDepJu & \aDepJuAll & \aDepJuI & \aDepJuII & \aDepJuIII & \aDepJuIV & \aDepJuV & \aDepJuVI & \aDepJuVII & \aDepJuVIII \tabularnewline
mnr & \aDepMnr & \aDepMnrAll & \aDepMnrI & \aDepMnrII & \aDepMnrIII & \aDepMnrIV & \aDepMnrV & \aDepMnrVI & \aDepMnrVII & \aDepMnrVIII \tabularnewline
Mmo & \aDepMo & \aDepMoAll & \aDepMoI & \aDepMoII & \aDepMoIII & \aDepMoIV & \aDepMoV & \aDepMoVI & \aDepMoVII & \aDepMoVIII \tabularnewline
nk & \aDepNk & \aDepNkAll & \aDepNkI & \aDepNkII & \aDepNkIII & \aDepNkIV & \aDepNkV & \aDepNkVI & \aDepNkVII & \aDepNkVIII \tabularnewline
oa & \aDepOa & \aDepOaAll & \aDepOaI & \aDepOaII & \aDepOaIII & \aDepOaIV & \aDepOaV & \aDepOaVI & \aDepOaVII & \aDepOaVIII \tabularnewline
oc & \aDepOc & \aDepOcAll & \aDepOcI & \aDepOcII & \aDepOcIII & \aDepOcIV & \aDepOcV & \aDepOcVI & \aDepOcVII & \aDepOcVIII \tabularnewline
pd & \aDepPd & \aDepPdAll & \aDepPdI & \aDepPdII & \aDepPdIII & \aDepPdIV & \aDepPdV & \aDepPdVI & \aDepPdVII & \aDepPdVIII \tabularnewline
pnc & \aDepPnc & \aDepPncAll & \aDepPncI & \aDepPncII & \aDepPncIII & \aDepPncIV & \aDepPncV & \aDepPncVI & \aDepPncVII & \aDepPncVIII \tabularnewline
ROOT & root of sentence & \aDepRootAll & \aDepRootI & \aDepRootII & \aDepRootIII & \aDepRootIV & \aDepRootV & \aDepRootVI & \aDepRootVII & \aDepRootVIII \tabularnewline
sb & \aDepSb & \aDepSbAll & \aDepSbI & \aDepSbII & \aDepSbIII & \aDepSbIV & \aDepSbV & \aDepSbVI & \aDepSbVII & \aDepSbVIII \tabularnewline
svp & separable verb prefix & \aDepSvpAll & \aDepSvpI & \aDepSvpII & \aDepSvpIII & \aDepSvpIV & \aDepSvpV & \aDepSvpVI & \aDepSvpVII & \aDepSvpVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

\textbf{category} & \textbf{examples} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\

@@

body & back, hip, shoulder; jacket, dress, shirt & \aDescrBodyAll & \aDescrBodyI & \aDescrBodyII & \aDescrBodyIII & \aDescrBodyIV & \aDescrBodyV & \aDescrBodyVI & \aDescrBodyVII & \aDescrBodyVIII \tabularnewline
bodypart  & arm, finger, leg, toe & \aDescrBodypartAll & \aDescrBodypartI & \aDescrBodypartII & \aDescrBodypartIII & \aDescrBodypartIV & \aDescrBodypartV & \aDescrBodypartVI & \aDescrBodypartVII & \aDescrBodypartVIII\tabularnewline
face & face, ear, nose, mouth & \aDescrFaceAll & \aDescrFaceI & \aDescrFaceII & \aDescrFaceIII & \aDescrFaceIV & \aDescrFaceV & \aDescrFaceVI & \aDescrFaceVII & \aDescrFaceVIII \tabularnewline
female & nurse, mother, woman & \aDescrFemaleAll & \aDescrFemaleI & \aDescrFemaleII & \aDescrFemaleIII & \aDescrFemaleIV & \aDescrFemaleV & \aDescrFemaleVI & \aDescrFemaleVII & \aDescrFemaleVIII \tabularnewline
females & women & \aDescrFemalesAll & \aDescrFemalesI & \aDescrFemalesII & \aDescrFemalesIII & \aDescrFemalesIV & \aDescrFemalesV & \aDescrFemalesVI & \aDescrFemalesVII & \aDescrFemalesVIII \tabularnewline
fname & Jenny & \aDescrFnameAll & \aDescrFnameI & \aDescrFnameII & \aDescrFnameIII & \aDescrFnameIV & \aDescrFnameV & \aDescrFnameVI & \aDescrFnameVII & \aDescrFnameVIII \tabularnewline
furniture & bench, bed, table, chair & \aDescrFurnitureAll & \aDescrFurnitureI & \aDescrFurnitureII & \aDescrFurnitureIII & \aDescrFurnitureIV & \aDescrFurnitureV & \aDescrFurnitureVI & \aDescrFurnitureVII & \aDescrFurnitureVIII \tabularnewline
geo & building, tree, street, alley, meadow, cornfield, river & \aDescrGeoAll & \aDescrGeoI & \aDescrGeoII & \aDescrGeoIII & \aDescrGeoIV & \aDescrGeoV & \aDescrGeoVI & \aDescrGeoVII & \aDescrGeoVIII \tabularnewline
geo-room & living room; wall, door, window, floor, turf & \aDescrGeoroomAll & \aDescrGeoroomI & \aDescrGeoroomII & \aDescrGeoroomIII & \aDescrGeoroomIV & \aDescrGeoroomV & \aDescrGeoroomVI & \aDescrGeoroomVII & \aDescrGeoroomVIII \tabularnewline
head & head, hair, ear, neck, helmet & \aDescrHeadAll & \aDescrHeadI & \aDescrHeadII & \aDescrHeadIII & \aDescrHeadIV & \aDescrHeadV & \aDescrHeadVI & \aDescrHeadVII & \aDescrHeadVIII \tabularnewline
male & man, father, soldier & \aDescrMaleAll & \aDescrMaleI & \aDescrMaleII & \aDescrMaleIII & \aDescrMaleIV & \aDescrMaleV & \aDescrMaleVI & \aDescrMaleVII & \aDescrMaleVIII \tabularnewline
males & boys, opponents & \aDescrMalesAll & \aDescrMalesI & \aDescrMalesII & \aDescrMalesIII & \aDescrMalesIV & \aDescrMalesV & \aDescrMalesVI & \aDescrMalesVII & \aDescrMalesVIII \tabularnewline
mname & Bubba, Kennedy & \aDescrMnameAll & \aDescrMnameI & \aDescrMnameII & \aDescrMnameIII & \aDescrMnameIV & \aDescrMnameV & \aDescrMnameVI & \aDescrMnameVII & \aDescrMnameVIII \tabularnewline
object & telephone, car & \aDescrObjectAll & \aDescrObjectI & \aDescrObjectII & \aDescrObjectIII & \aDescrObjectIV & \aDescrObjectV & \aDescrObjectVI & \aDescrObjectVII & \aDescrObjectVIII \tabularnewline
objects & wheels, photos & \aDescrObjectsAll & \aDescrObjectsI & \aDescrObjectsII & \aDescrObjectsIII & \aDescrObjectsIV & \aDescrObjectsV & \aDescrObjectsVI & \aDescrObjectsVII & \aDescrObjectsVIII \tabularnewline
persons & hippies, patients & \aDescrPersonsAll & \aDescrPersonsI & \aDescrPersonsII & \aDescrPersonsIII & \aDescrPersonsIV & \aDescrPersonsV & \aDescrPersonsVI & \aDescrPersonsVII & \aDescrPersonsVIII \tabularnewline
setting\_new & on a ``bridge'', on an ``alley'', on ``campus'' & \aDescrSettingnewAll & \aDescrSettingnewI & \aDescrSettingnewII & \aDescrSettingnewIII & \aDescrSettingnewIV & \aDescrSettingnewV & \aDescrSettingnewVI & \aDescrSettingnewVII & \aDescrSettingnewVIII \tabularnewline
setting\_rec & at the ``bus stop'' & \aDescrSettingrecAll & \aDescrSettingrecI & \aDescrSettingrecII & \aDescrSettingrecIII & \aDescrSettingrecIV & \aDescrSettingrecV & \aDescrSettingrecVI & \aDescrSettingrecVII & \aDescrSettingrecVIII \tabularnewline
